Two applications of logic programming to Coq

### 2020-11-06 papers/types2020/sec3.tex
Finished a first pass over Sections 3 and 4.  I give up the lock on section 3.  I wish to continue with Section 4 a bit more.

\newpage

To illustrate a proof certificate format that uses this richer logic
and proof system, consider the simple \lP code in
Figure~\ref{fig:debruijn}.  Using the constants provided in that
figure, the untyped $\lambda$-term
$\lambda x (x (\lambda y (y (\lambda z (x (\lambda u\,z))))))$ can be
encoded as the following Elpi term of type \lsti{deb}.
%
\begin{lstlisting}[basicstyle=\ttfamily,language=lprolog]
(lambda (apply 0 [lambda (apply 0 [lambda (apply 2 
                                                    [lambda (apply 1 [])])])]))
\end{lstlisting}

 presents the specific FPC that defines the
proof semantics of using the De Bruijn notions for untyped
$\lambda$-terms as proof evidence of a proof in intuitionistic
propositional logic.

This FPC can be interpreted by the proof
certificate checker in the file \verb+ljf-dep.mod+ of the repository
\url{https://github.com/proofcert/fpc-elpi/}.
We note that this proof certificate checker is also able to
simulataneously synthesize a Coq proof term while checking (see
Section~\ref{}) all the while remaining less than 90 lines of Elpi
code.

  That FPC definition, along with a proof checker
capable of synthesizing Coq proof terms during proof checker, makes it
possible to use the term denoting the

@@

\newpage

@@

% LocalWords:  backchaining disjunct LJT dep qheight qsize orE someE
% LocalWords:  Elpi modularity Herbelin bc PTSC's dprolog CIC init lp
% LocalWords:  Andreoli's basicstyle lprolog sigs Coq's sortedness Ev
% LocalWords:  backchain gref indt indc coq dest unfoldings str fpc
% LocalWords:  evar nat forall ys elpi Qed

>>>>

To illustrate a proof certificate format that uses this richer logic
and proof system, consider the simple \lP code in
Figure~\ref{fig:debruijn}.  Using the constants provided in that
figure, the untyped $\lambda$-term
$\lambda x (x (\lambda y (y (\lambda z (x (\lambda u\,z))))))$ can be
encoded as the following Elpi term of type \lsti{deb}.
%
\begin{lstlisting}[basicstyle=\ttfamily,language=lprolog]
(lambda (apply 0 [lambda (apply 0 [lambda (apply 2 
                                                    [lambda (apply 1 [])])])]))
\end{lstlisting}
Using the constructor \lsti{lc} and \lsti{args}, terms in De Bruijn
syntax (terms of type \lsti{deb}) are incorporated into proof
certificates (terms of type \lsti{cert}) along with other integer
arguments that are needed to compute offsets to address bound
variables.  
%
This FPC can be interpreted by the proof certificate checker in the
file \verb+ljf-dep.mod+ of the repository
\url{https://github.com/proofcert/fpc-elpi/}.  We note that this proof
certificate checker is also able to simultaneously synthesize a Coq
proof term while checking (see Section~\ref{sec:elab}) all the while
remaining less than 90 lines of Elpi code.

@@

@@

% LocalWords:  backchaining disjunct LJT dep qheight qsize orE someE
% LocalWords:  Elpi modularity Herbelin bc PTSC's dprolog CIC init lp
% LocalWords:  Andreoli's basicstyle lprolog sigs Coq's sortedness Ev
% LocalWords:  backchain gref indt indc coq dest unfoldings str fpc
% LocalWords:  evar nat forall ys elpi Qed lc args ljf
